---
title:"Example Rmd Report"
author:" Mark and Udari"
output:html_document
theme:cosmo
---

## Heading number 1 -download file and read into R
Here we're using the 'download.file()' command to obtain the dataset
then we're reading it into R.It is important to set the 'header = TRUE' and 'row.names =1 so that the data is formatted properly'
```{r,chunk1,echo=TRUE}
#Download the data
download.file("https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/mydata.tsv",destfile = "mydata.tsv")

#Read into R making sure the 1st column is set as the row names and headers are recognized
x <-read.table("mydata.tsv",header =TRUE,stringsAsFactors = FALSE, row.names = 1)
```
## Heading 2 - checking data integrity
Here we use the 'head()'command to look at the first 6 lines of the data frame, then 'str()' to make sure that the contents are recognised as numeric

```{r,chunk2,echo=TRUE}
# Lets check if the data has been imported properly
head(x)

# check data structure
str(x)
